### 2018-04-16 README.Rmd
Minor fixes (#32)
* update readme and site

* update pkgdown site; re-style; ggsci for colors

* update pkgdown; tweak CI params

__Author:__ [Nima Hejazi](http://nimahejazi.org)

@@

For standard use, install from [Bioconductor](https://bioconductor.org):

@@

For details on how to best use `methyvim` to perform data-adaptive estimation
and obtain nonparametric inference in the context of differential methylation
analyses, please consult the most recent [package vignette](http://bioconductor.org/packages/release/bioc/vignettes/methyvim/inst/doc/using_methyvim.html)
available through the [Bioconductor
project](https://bioconductor.org/packages/methvim).

@@

It is our hope that `methyvim` will grow to be widely adopted as a tool for the
nonparametric assessment of variable importance in studies of differential
methylation. To that end, contributions are very welcome, though we ask that
interested contributors consult our [`contribution
guidelines`](https://github.com/nhejazi/methyvim/blob/master/CONTRIBUTING.md)
prior to submitting a pull request.

>>>>

__Author:__ [Nima Hejazi](https://nimahejazi.org)

@@

For standard use, install from
[Bioconductor](https://bioconductor.org/packages/methyvim):

@@

For details on how to best use the `methyvim` R package, please consult the most
recent [package
vignette](http://bioconductor.org/packages/release/bioc/vignettes/methyvim/inst/doc/using_methyvim.html)
available through the [Bioconductor
Project](https://bioconductor.org/packages/methvim).

@@

Contributions are very welcome. Interested contributors should consult our
[contribution
guidelines](https://github.com/nhejazi/methyvim/blob/master/CONTRIBUTING.md)
prior to submitting a pull request.
